Neuro I

### 2017-09-13 neuro1.rmd
sed -i 's/=>/$\rightarrow$/g' *
not sure what I did

---
title: "Neuro I"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
urlcolor: blue
---

@@

Tinels sign: tap over nerve => if tingly/pins & needles => nerve irritation. Over time, expect the tingly feeling to go downwards more and more to show the nerve is healing.

>>>>

---
title: "Neuro I"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
fontsize: 11pt
urlcolor: blue
---

@@

Tinels sign: tap over nerve $\rightarrow$ if tingly/pins & needles $\rightarrow$ nerve irritation. Over time, expect the tingly feeling to go downwards more and more to show the nerve is healing.
